Homework Report

### 2017-01-30 work/work.tex
Starting to move towards proposition structure

\section*{Construct a graph}
Construct a simple graph, \(G = (V, E)\), such that:

@@

Let \(\chi\) refer to the coloring generated by \emph{heuristic B}. Let \(\chi^{*}\) be the optimal coloring.

@@

\section*{Upper Bounds}
Examine the upper bounds of the greedy heuristic and the greedy plus degree sequencing heuristic. \newline

To do so, let's create another example that satisfies conditions \((1)\) and \((2)\) from above. After doing some research into bipartite graphs, I learned that \emph{crown graphs} are excellent at showing how bad greedy heuristics can be, as shown and defined in \cite{kordecki}.

@@

We can see that \(\Delta(G) = 4\). We can also see \(d(v) = 4\) for all \(v \in V\). Thus, in both heuristics, the greedy algorithm would pick an order arbitrarily. We can show using this crown graph the worst-case scenario of these heuristics.

\begin{figure}[H]
\centering
\includegraphics[scale=0.38]{images/graph-5.png}
\caption{Worst-case coloring of \(H\) using either greedy heuristic}
\end{figure}

@@

\subsection*{In General}

Let \(P = (V, E)\) be a simple, complete graph. \newline

>>>>

\section*{Findings}

\begin{prop}
Heuristic A and Heuristic B do not always produce an optimal solution, i.e. they do not always produce a minimum coloring of a graph.
\end{prop}

I will show this for \emph{heuristic B}. It is trivial to show the same for \emph{heuristic A} as \emph{heuristic B} includes the same steps as \emph{heuristic A}. I will construct a simple graph, \(G = (V, E)\), such that:

@@

Let \(\chi\) refer to the coloring of \(G\) generated by \emph{heuristic B}. Let \(\chi^{*}\) be the optimal coloring of \(G\).

@@

\begin{prop}
Heuristic A and heuristic B have an upper bound of \(\Delta + 1\).
\end{prop}

To show this, I will create another example that satisfies conditions \((1)\) and \((2)\) from above. After doing some research into bipartite graphs, I learned that \emph{crown graphs} are excellent at showing how bad greedy heuristics can be, as shown and defined in \cite{kordecki}.

@@

We can see that \(\Delta(G) = 4\). We can also see \(d_G(v) = 4\) for all \(v \in V\). Thus, in both heuristics A and B, the greedy algorithm would pick an order arbitrarily. We can show using this crown graph the worst-case scenario of these heuristics.

\begin{figure}[H]
\centering
\includegraphics[scale=0.38]{images/graph-5.png}
\caption{Worst-case coloring of \(H\) using either heuristic A or B}
\end{figure}

@@

\textbf{In General}: Let's take a look at how this looks in general. Let \(P = (V, E)\) be a simple, complete graph. \newline
